---
title: "Assignment 8 -- Kara Bonham"
output: html_notebook
---
###Load the *gapminder* and *tidyverse* libraries:
```{r}
# install.packages("gapminder")
# install.packages("tidyverse")
library(gapminder)
library(tidyverse)
```


###Summarized *gapminder* data:
```{r}
data("gapminder")
summary(gapminder)
```

###The `attach()` function
I have used the `attach()` function to skip using the name of the dataframe in every line and just reference the variables within gapminder from here on.
```{r}
attach(gapminder)
```


###Histogram and Scatterplot:
```{r}
hist(log(pop))
```
```{r}
plot(lifeExp ~ log(gdpPercap))
```


###A t-test of life-expectancy differences between South Africa and Ireland:
```{r}
df1 <- gapminder %>% 
  select(country, lifeExp) %>% 
  filter(country == "South Africa" |
           country == "Ireland")
t.test(data = df1, lifeExp ~ country)
```
The p-value is 4.466e-09, which is less than 0.05, which means the difference in life expectancy between Ireland and South Africa is significantly different.


###Life Expectancy vs. gdp-per-capita:
```{r}
gapminder %>%
  filter(gdpPercap < 50000) %>%
  ggplot(aes(x=log(gdpPercap), y=lifeExp, col=continent, size=pop))+
  geom_point(alpha=0.3)+
  geom_smooth(method = lm)
```


###Faceted plot:
```{r}
gapminder %>%
  filter(gdpPercap < 50000) %>%
  ggplot(aes(x=log(gdpPercap), y=lifeExp, col=year, size=pop))+
  geom_point(alpha=0.3)+
  geom_smooth(method = lm)+
  facet_wrap(~continent)
```


###Linear model test of life expectancy by gdp-per-capita and population:
```{r}
summary(lm(lifeExp ~ gdpPercap+pop))
```





